---
title: "Deal_with_fam"
author: "Hsiao"
date: "7/7/2021"
output: html_document
---

Clean the data and check coherent

1. Relationships : 
Benchmark 2007
2003: identical
1999: almost identical ( despite lack of 0:none, 1:self, which are not important)
1996: almost identical ( 97:家人->養媳，但應該非常少見)
1993 : 前段大部分一致（么兒、么女除外）。混亂

88: not applicable, 99: missing

2. Gender : 
1:Male, 2:Female, 8: Not Applicable, 9: missing

3. Age : 
[0:99], 88;not applicable, 99: missing

4: Edu : (6 yo up)
Benchmark 2007
2003: + 18博士
1999: identical 
1996: 沒有空中大學系列

5: work: 6up
benchmark 2007 : 88不適用, 98不知道, 99 missing
2003 : 8不適用, 9 missing
1999 : 同2003
1996 : 同2003

6: marstat : identical 

7: livstat : 
benchmark 2007
2003 : identical 
1999: 2求學+工作, 3兵役, 4其他 ！要改 ( unsolve)
1996: 1一直住家裡, 2求學, 3兵役, 4工作, 7其他 不同住：0

8. livwhere ：
9. meet: idetical 
10. tele: almost identical 

```{r}
fam<- rbind(fam_96, fam_99, fam_03, fam_07)

table(sort(fam$relationship))
table(sort(fam_07$gender)) # gender ==3 出現在07年，就是泛稱的家人
table(sort(fam$age))
hist(fam$age)
table(sort(fam$edu))
fam[,work:= ifelse(fam$work ==8, 88, work)]
table(sort(fam$work))
table(sort(fam$marstat)) # 88 算15歲以下， 之前的88是算6歲以下
fam[,livwhere:= ifelse(fam$livwhere ==8, 0, livwhere)] # 不適用者是住家裡
table(sort(fam$livstat))
table(sort(fam$livwhere))
fam[,meet:= ifelse(fam$meet ==88, 0, meet)] # 不適用者是住家裡
fam[,tele:= ifelse(fam$tele ==88, 0, tele)] # 不適用者是住家裡
table(fam$meet)
table(fam$tele)

fam[survey_year ==1999, livstat:= ifelse(fam[survey_year==1999]$livstat ==4, 5, fam[survey_year==1999]$livstat)]
fam[survey_year ==1999, livstat:= ifelse(fam[survey_year==1999]$livstat ==3, 4, fam[survey_year==1999]$livstat)] # 3: 因為工作而住在外面，被混在2裡面 當年coding問題
table(sort(fam[survey_year==1999, ,]$livstat))

write.table(fam, file = "fam_v2.csv", sep = ",")

```



```{r}
# matching 

fam<- read.csv("/Users/Ano/Desktop/HRS_Chao/TSLA/fam_v2.csv")






```
